\section{Sustainability report}

\subsection{Self-assessment of the current domain of sustainability competition}

\justify
The sustainability is a field where I was not conscious to think about but indeed I did.  

\justify
I'm always thinking on the social and economical aspects of my projects as I'm interested on this fields. A common question I use to ask myself is how this project will affect the society? This is obviously thinking about the social and the economical aspects. Non-ethical technological products are becoming a tendency, changing people vote intention, governments tracking its citizens are examples of this and examples of developers that not thought about the social and economical aspects of their projects.

\justify
I have been ignoring or keeping apart thinking on the environmental aspects of my projects. This is usually because my projects don't use to impact on this aspect but now that I think that is the most important topic to think about it. At least on High-performance computing field that aims to solve or to find faster the solution to the problem.

\justify
I have also the concern to use and promote the free (as in freedom) software and hardware to avoid companies to be able to modify lifetime of products and therefore, generate more e-waste.

\subsection{Economic Dimension}

\subsubsection{Reflection on the cost estimated}

\justify
The cost estimated it is not precise as some parts are omitted for confidentiality. The estimations I made try to be realistic with the current price standard in Barcelona, Spain but I'm almost sure I miss predicted some estimations as I'm not experienced on this also not in charge of making the expenses.

\subsubsection{Useful Life}
\justify
My project aims to improve the computation time of a simulation. Hopefully if we improve the simulation the computation times will be lesser, therefore, scientists will have to invert less money on computational resources or will reach faster to conclusion which leads to scientific progress. 

\subsection{Environmental Dimension}

\subsubsection{Environmental impact of the project development}

\justify
The environmental impact estimation has not been done. It is a very complex calculation as it involves the MareNostrum4 fabrication and electrical consumption and it is used by a lot of users. Scoping this in the project means making a lot of estimations which is not possible.

\subsubsection{Minimize environmental impact}

\justify
This is not possible in the project. The machine is already built.

\justify
The only way we can act is in being conscious the electricity that consumes the machine and the laptop and try to use efficient the resources. This implies performing the appropriate number of runs.

\subsubsection{Environmental impact of the project}

\justify
The project will have a positive environmental impact. This research will be useful in order to make programs more efficient and reduce the running time of the applications which implies less power consumption.

\subsection{Social Dimension}

\subsubsection{Personal growth}

\justify
This project will make me grow on my young research career and will make me improve me technical and social skills. Contacting and explaining the project to the application developers, analysing, thinking and developing an optimal solution, discussing with my project manager all the aspects of the project, writing technical reports are things that will make me grow as a professional and as person.

\subsubsection{Social improvement}

\justify
This project aims to accelerate the combustion research as its objective is to make the scientific simulation to go faster. This can impact the society in many ways, from making less pollute motors to making faster planes. We cannot predict what research we will accelerate. 

\subsubsection{Is there a real need for the project?}

\justify
There is a need to improve this simulations because they are really slow. A solution is needed and we can provide a step towards this. 
